Sample size

### 2021-05-03 scripts/r/sample-size/sample-size.Rmd
:chart_with_upwards_trend: - generate plot of sample size simulations

```{r plot}
sample_cri <- sample_sims %>%
  unnest(sd_team) %>%
  mutate(sd_team = unlist(sd_team)) %>% 
  filter(sd_team > 0) %>%
  rename(cri = sd_team)

labels <- tibble(
  x = c(0.5, 0.25, 0.9, 0.3, 1.3),
  y = c(1.25, 0.7, 1.5, 0.1, 1.15),
  labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
)

arrows <- tibble(
    x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
    y1 = c(1.15, 0.6, 1.4, 0.1, 1.2),
    x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
    y2 = c(0.8, 0.45, 1.2, 0.1, 1.39)
  )

>>>>

```{r plot}
sample_cri <- sample_sims %>%
  mutate(
    cri = as.numeric(map(sd_team, ~.x[[1]])),
    cri_sd = as.numeric(map(sd_team, ~.x[[2]]))
  )

labels <- tibble(
  x = c(0.5, 0.25, 0.9, 0.3, 1.3),
  y = c(1.25, 0.7, 1.5, 0.1, 0.9),
  labs = c("Mean", "1st quart.", "3rd quart.", "Min", "Max")
)

arrows <- tibble(
    x1 = c(0.5, 0.25, 0.9, 0.25, 1.3),
    y1 = c(1.15, 0.6, 1.4, 0.1, 1),
    x2 = c(0.63, 0.33, 0.97, 0.05, 1.33),
    y2 = c(0.8, 0.45, 1.2, 0.1, 1.2)
  )
